The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-10-03 paper/ms.tex
remove hd 189636

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, the majority of which were previously entirely missing. Sixteen stars were to some extent observed conventionally: HD~174020 was targeted in LC for Q2, 6, 10, and 14; HD~175841 for Q11-12, 14-16, with SC for Q3; HD~176582 for Q12-13; HD~178090 for Q1, 3, and 10; HD~180682 for Q0, 3, and 7; HD~181069 for Q1, 10, 13, 14, and 17; HD~181878 for Q14-17; HD~182694 for Q2; HD~183124 for even quarters; HD~185351 for Q1-3 and with SC for Q16; HD~186155 for only Q1; HD~187217 for Q14-17; HD~188252 for only Q13; HD~189013 with SC for Q3 as a $\gamma$~Dor; V380~Cyg for Q11 and with SC for Q7, 9, 10, 12-17; and V819~Cyg for Q14, 16 and 17. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy. A Venn diagram of the sample, noting the availablilty of asteroseismic fits Section~\ref{asteroseismology} and spectroscopy (Section~\ref{spectroscopy}) is displayed in Figure~\ref{venn}. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.

@@

\begin{figure}
\noindent\includegraphics[width=8cm,keepaspectratio]{venn.png}
\caption{\label{venn}
Venn diagram showing the overall structure of the \kepler Smear Campaign sample, showing the subsets for which TRES spectroscopy and asteroseismology are available and their overlap.}
\end{figure}

>>>>

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, the majority of which were previously entirely missing. Sixteen stars were to some extent observed conventionally: HD~174020 was targeted in LC for Q2, 6, 10, and 14; HD~175841 for Q11-12, 14-16, with SC for Q3; HD~176582 for Q12-13; HD~178090 for Q1, 3, and 10; HD~180682 for Q0, 3, and 7; HD~181069 for Q1, 10, 13, 14, and 17; HD~181878 for Q14-17; HD~182694 for Q2; HD~183124 for even quarters; HD~185351 for Q1-3 and with SC for Q16; HD~186155 for only Q1; HD~187217 for Q14-17; HD~188252 for only Q13; HD~189013 with SC for Q3 as a $\gamma$~Dor; V380~Cyg for Q11 and with SC for Q7, 9, 10, 12-17; and V819~Cyg for Q14, 16 and 17. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.

@@

% \begin{figure}
% \noindent\includegraphics[width=8cm,keepaspectratio]{venn.png}
% \caption{\label{venn}
% Venn diagram showing the overall structure of the \kepler Smear Campaign sample, showing the subsets for which TRES spectroscopy and asteroseismology are available and their overlap.}
% \end{figure}
